---
title: "Statistical Inference Course Project"
Author Name: Farren Tang
output: html_document
---

#### Overview
This project is spilt into 2 parts. They will be spilt into simulation and statistical analysis of tooth growth data. 
For the simulation part, we will investigate the exponential distribution in R and compare it with the Central Limit Theorem.
For the statistical analysis, we will see if there are significant differences in the means of using OJ or VC in the tooth growth dataset. 

```{r, Loading of data, echo = FALSE}
library(ggplot2)
```


### Part 1: Simulation 
##### A. Mean
Simulated mean is the barchart - in this case is 5 -5.2, since most of the observations are clustered near 5. 
Theoretical mean is the black line - in this case is 5, because the theoretical mean is 5   
```{r, Simulation}
mns = NULL
for (i in 1 : 1000) mns = c(mns, mean(rexp(1000, 0.2)))
ggplot() +geom_histogram(aes(mns), bins = 10, fill ="grey40") +
        geom_vline( xintercept = 5)
```  

##### B. Variance  
Theoretical variance is the black line - in this case is 5, because the theoretical variance is 5 

```{r, Variance}
mns = NULL
for (i in 1 : 1000) mns = c(mns, mean(rexp(1000, 0.2)))
ggplot() +geom_density(aes(mns))+
        geom_vline( xintercept = 5)

```

From the density and histogram, we can see that it is approx normal, since they concentrate near the mean, and is approximately symmetrical about the mean.

