---
title: "Statistical Inference Course Project"
output: html_document
Author Name: Farren Tang
---

#### Overview
This project is spilt into 2 parts. They will be spilt into simulation and statistical analysis of tooth growth data. 
For the simulation part, we will investigate the exponential distribution in R and compare it with the Central Limit Theorem.

```{r, Loading of data, echo = FALSE}
library(ggplot2)
```


### Part 1: Simulation 
##### A. Mean

```{r, Simulation}
lambda = 0.2
mean_exp = 1/lambda
sd_exp = 1/lambda
sim_mat <- matrix(rexp(1000*40, lambda), nrow = 1000, ncol = 40)
Meandist <- apply(sim_mat, 1, mean)
hist(Meandist)
abline(v = 1/lambda, lty = 1, lwd = 5, col = "blue")

```  
Simulated mean is the barchart - in this case is `r mean(Meandist)`
Theoretical mean is the blue line `r mean_exp`

##### B. Variance  
```{r, Variance}
vardist <- apply(sim_mat, 1, var)
hist(vardist)
abline(v = mean(vardist), lty = 1, lwd = 5, col = "blue")

#theoretical variance
(1/lambda)^2
#sample variance
mean(vardist)
```


Theoretical variance is the black line - in this case is 5, because the theoretical variance is `r (1/lambda)^2` 
Sample variance is `r mean(vardist)` 
Thus, they are quite close.

From the density and histogram, we can see that it is approx normal, since they concentrate near the mean, and is approximately symmetrical about the mean.

